Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-06-17 manuscripts/manuscript.Rmd
update manuscript to write out figure data

library("methods")
library("knitr")
basename <- "manuscript"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)
# PDF-based figures
opts_chunk$set(dev='pdf')
fig.cache <- FALSE

@@

@@

fig2_df <- as.data.frame(subset(dt, replicate=='rep_1'))
fig2_df <- fig2_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn")]
fig2_df <- melt(fig2_df, id = c("time", "penalty_fn"))
fig2_df <- data.frame(fig2_df, baseline = fig2_df$variable)
variable_map <- c(fishstock = "fish_stock", alternate = "fish_stock", harvest = "harvest", harvest_alt = "harvest")
baseline_map <- c(fishstock = "penalty", alternate = "no_penalty", harvest = "penalty", harvest_alt = "no_penalty")
fig2_df$variable <- variable_map[fig2_df$variable]
fig2_df$baseline <- baseline_map[fig2_df$baseline]

ggplot(fig2_df, aes(time, value, col=baseline)) +
  geom_line() +
  facet_grid(variable~penalty_fn) + 
  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")

@@

@@

```{r Figure_5}
ggplot(hist_dat) + geom_density(aes(value, fill=variable), alpha=0.6)+facet_wrap(~penalty_fn)
```

@@

```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.  All values are relative to the cost-free adjustment optimum, NPV0.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present. The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs."}
table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
table1_long$reduction <- as.factor(table1_long$reduction)
ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + facet_wrap(~reduction) 
```

@@

ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, scales="free_y") 
```

>>>>

library("methods")
library("knitr")
basename <- "manuscript"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)
# PDF-based figures
opts_chunk$set(dev='pdf')
fig.cache <- TRUE

@@

write.csv(dt, "components/data/100reps.csv")
write.csv(fees, "components/data/figure2.csv")

@@

fig3_df <- as.data.frame(subset(dt, replicate=='rep_1'))
fig3_df <- fig3_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn")]
fig3_df <- melt(fig3_df, id = c("time", "penalty_fn"))
fig3_df <- data.frame(fig3_df, baseline = fig3_df$variable)
variable_map <- c(fishstock = "fish_stock", alternate = "fish_stock", harvest = "harvest", harvest_alt = "harvest")
baseline_map <- c(fishstock = "penalty", alternate = "no_penalty", harvest = "penalty", harvest_alt = "no_penalty")
fig3_df$variable <- variable_map[fig3_df$variable]
fig3_df$baseline <- baseline_map[fig3_df$baseline]

ggplot(fig3_df, aes(time, value, col=baseline)) +
  geom_line() +
  facet_grid(variable~penalty_fn) + 
  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")

write.csv(fig3_df, "components/data/figure3.csv")
```

@@

write.csv(figure4_df, "components/data/figure4.csv")
```

@@

```{r Figure_5}
ggplot(hist_dat) + geom_density(aes(value, fill=variable), alpha=0.6)+facet_wrap(~penalty_fn)
write.csv(hist_dat, "components/data/figure5.csv")
```

@@

```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.  All values are relative to the cost-free adjustment optimum, NPV0.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present. The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs."}
table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
table1_long$reduction <- as.factor(table1_long$reduction)
ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + facet_wrap(~reduction) 
write.csv(table1_long, "components/data/figure6.csv")
```

@@

ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, scales="free_y")

write.csv(table2_long, "components/data/figure7.csv")
```
